Automatic Matching of Bullet Lands

### 2016-11-30 imaging-paper.tex
Missed the tex file

\section{Evaluation}
In order to get a better understanding of  how  the matching algorithm works in known matches and non-matches, we investigate its performance in a test scenario based on the James Hamby study.
As a first step, we automatically assess the quality of each of the lands by  checking that we can identify a stable region on each land. For this, we compute the cross-correlation of signatures extracted from heights 25$\mu m$ apart. For a stable region, we require a minimum of 0.95 for the cross correlation. Four lands from different bullets are flagged as problematic in this respect. A visual inspection (see Figure~\ref{fig:fourflags}) shows that each one of these lands has scratch marks across the surface, also known as `tank rash'.
%
\begin{figure}
  \centering
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Barrel 6 Bullet 2-1}
%' <<echo=FALSE>>=
%' b1 <- read.x3p(file.path(datadir, "Br6 Bullet 2-1.x3p"))
%' image(b1$surface.matrix)
%' @
\includegraphics[width=\textwidth]{images/br6-2-1-grey.png}
\end{subfigure}
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Barrel 9 Bullet 2-4}
\includegraphics[width=\textwidth]{images/br9-2-4-grey.png}
\end{subfigure}
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Unknown Bullet B-2}
\includegraphics[width=\textwidth]{images/b-2-grey.png}
\end{subfigure}
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Unknown Bullet Q-4}
\includegraphics[width=\textwidth]{images/q-4-grey.png}
\end{subfigure}
\caption{\label{fig:fourflags}Images of the four lands that got flagged during the quality assessment. All of them show scratch marks (tank rash) across the striation marks from the barrel. They are excluded from the remainder of the analysis.}
\end{figure}
%
We exclude these four lands from further matching considerations and
 run all remaining lands from the unknown bullets against all remaining lands from known bullets for matches, i.e. we are comparing $15 \times 6 -2 = 90 - 2 = 88$ lands from unknown bullets against $2 \times 10 \times 6 -2 = 120 - 2 = 118$ lands from known bullets, yielding a total of $10,384$ land-to-land comparisons. Out of these comparisons, there are 172 known matches (KM), while the rest are known non-matches (KNM). 
 When things go well, they look like the results in Figure~\ref{fig:hamby-perfect}: Figure~\ref{fig:hamby-perfect}a shows the distribution of the number of maximum consecutive matching striae between land C-3 and all 118 lands from known bullets. Two lands show a high CMS. These correspond to the known matches with C-3, shown in Figures~\ref{fig:hamby-perfect}b and~\ref{fig:hamby-perfect}c. 
 Unfortunately, not all results are as clear cut. 
It might not be reasonable to assume that we can match all lands, but the idea is to try to maximize the number of matches to get an overview of what we might be able to expect from an automated match.

\begin{figure}[hbtp]
\begin{subfigure}[t]{\textwidth}\centering
\caption{Maximal number of CMS between unknown bullet C-3 and all of the other 118 considered (known) lands. For two lands the number of maximum CMS is high. }
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=.5\textwidth]{figure/cms-1}

>>>>

\section{Evaluation}
In order to get a better understanding of  how  the matching algorithm works in known matches and non-matches, we investigate its performance in a test scenario based on the James Hamby study.
As a first step, we automatically assess the quality of each of the lands by  checking that we can identify a stable region on each land. For this, we compute the cross-correlation of signatures extracted from heights 25$\mu m$ apart. For a stable region, we require a minimum of 0.95 for the cross correlation. Four lands from different bullets are flagged as problematic in this respect. A visual inspection (see Figure~\ref{fig:fourflags}) shows that each one of these lands has scratch marks across the surface, also known as `tank rash'.
%
\begin{figure}
  \centering
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Barrel 6 Bullet 2-1}
%' <<echo=FALSE>>=
%' b1 <- read_x3p(file.path(datadir, "Br6 Bullet 2-1.x3p"))
%' image(b1$surface.matrix)
%' @
\includegraphics[width=\textwidth]{images/br6-2-1-grey.png}
\end{subfigure}
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Barrel 9 Bullet 2-4}
\includegraphics[width=\textwidth]{images/br9-2-4-grey.png}
\end{subfigure}
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Unknown Bullet B-2}
\includegraphics[width=\textwidth]{images/b-2-grey.png}
\end{subfigure}
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Unknown Bullet Q-4}
\includegraphics[width=\textwidth]{images/q-4-grey.png}
\end{subfigure}
\caption{\label{fig:fourflags}Images of the four lands that got flagged during the quality assessment. All of them show scratch marks (tank rash) across the striation marks from the barrel. They are excluded from the remainder of the analysis.}
\end{figure}
%
We exclude these four lands from further matching considerations and
 run all remaining lands from the unknown bullets against all remaining lands from known bullets for matches, i.e. we are comparing $15 \times 6 -2 = 90 - 2 = 88$ lands from unknown bullets against $2 \times 10 \times 6 -2 = 120 - 2 = 118$ lands from known bullets, yielding a total of $10,384$ land-to-land comparisons. Out of these comparisons, there are 172 known matches (KM), while the rest are known non-matches (KNM). 
 When things go well, they look like the results in Figure~\ref{fig:hamby-perfect}: Figure~\ref{fig:hamby-perfect}a shows the distribution of the number of maximum consecutive matching striae between land C-3 and all 118 lands from known bullets. Two lands show a high CMS. These correspond to the known matches with C-3, shown in Figures~\ref{fig:hamby-perfect}b and~\ref{fig:hamby-perfect}c. 
 Unfortunately, not all results are as clear cut. 
It might not be reasonable to assume that we can match all lands, but the idea is to try to maximize the number of matches to get an overview of what we might be able to expect from an automated match.

\begin{figure}[hbtp]
\begin{subfigure}[t]{\textwidth}\centering
\caption{Maximal number of CMS between unknown bullet C-3 and all of the other 118 considered (known) lands. For two lands the number of maximum CMS is high. }
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning in readChar(con, 5L, useBytes = TRUE): cannot open compressed file 'data/data-25-25/unkn9.RData', probable reason 'No such file or directory'}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in readChar(con, 5L, useBytes = TRUE): cannot open the connection}}\end{kframe}
\includegraphics[width=.5\textwidth]{figure/cms-1}
